---
title: "Delayed Discharge Bed Days"
output: html_document
editor_options: 
  chunk_output_type: console
---

**CAVEATS:**

Data Source: Delayed discharges in NHSScotland monthly up to January 2022.

Delayed discharge bed day rates are reported separately for Standard delays and Code 9 delays for those aged 18+ and are based on HSCP of residence.

Greater Glasgow and Clyde figures (GGC HSCPs) are the sum of all six GGC HSCPs and are based on residents of NHSGGC only.

Rates are calculated using the NRS Mid-Year Population Estimates for those aged 18+ (2020 population estimates are used for calculating the 2021/22 rates).

Scotland figures are an aggregate of local authority data, along with data reported under ‘Other’ responsible local authority (not applicable for Code 9s).


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.width = 10, fig.height = 6)
```


```{r include = "FALSE"} 
if(!require(librarian)){
  install.packages("librarian")
  library(librarian)
}

librarian::shelf(tidyverse, here, fs, rvest ,xml2, openxlsx, lubridate, readxl, janitor, glue, plotly, ggtext, kableExtra, gt, rlang)
source(here::here("scripts", "my_funcs.R"))
source(here::here("scripts", "populations.R"))
```

```{r variables}
Report_month <- "January"
Report_year <- 2022

# Current FY
fydate <- convert_calender_to_FY(Report_year, Report_month)
fydate_text <- seperate_years_by_slash(fydate)

# council areas of interest
CA_of_interest <- c("Scotland", "East Dunbartonshire", "East Renfrewshire", "Glasgow City", "Inverclyde", "Renfrewshire", "West Dunbartonshire") %>% 
  set_names(.)

CA_no_Scotland <- c("East Dunbartonshire", "East Renfrewshire", "Glasgow City", "Inverclyde", "Renfrewshire", "West Dunbartonshire") %>% 
  set_names(.)

CNeeds_list <- c("Code 9", "Standard") %>%
  set_names(.)
```


```{r historical-stats}
# getLAPops acquires pop data stored in an .rds file
#find pops for ages>= 18 for all LAs and Scotland
# NO SCOTLAND POP DATA WITH THIS .RDS

# no data available for mid-pop estimate for 2021.  
# locf (last observation carried forward) utilised from 2020 for 2021
#Scotland pop values created by summing all CouncilAreas.
LA_pop_18plus <- getLAPops(age_lowest = 18)

```

```{r download-NRS-recent-data}
#file downloaded from NRS website if filename not present in data folder
data_filename <- "beddays"
#if(!file_exists(here::here("data", glue("{data_filename}.xlsx")))){
download_data(filename = data_filename, month=Report_month, year=Report_year)

```

```{r convert-to-tibbles}
# save pathname of beddays xlsx file to object 
xl_file <- here::here("data", glue("{data_filename}.xlsx"))

#create a single tibble containing both healthboard and LA data, as "Scotland" located in HB... sheets. Only "Scotland" kept from HB... sheets 
# change format of FY (eg 1718)to year of start FY (2017)
raw_tib <- map_dfr(create_sheetname_vector(xl_file), # vector of LA and HB data from FY 12/13 until 21/22
              ~create_FY_authority(xl_file, sheet_name = .x)) 

######################################################################################
#create tibble with FY to date 
# tib_fytd <- raw_tib %>% 
#   select("CouncilArea", "AgeGroup", "ComplexNeedsFlag", "FYToDate", "FY", "FY_begin") %>% 
#   rename(Counts = FYToDate) %>% 
#   add_GGC_field()

######################################################################################
#create tibble with Month/Year Counts
# used to 1- select columns for pivoting & 2- set order of months
month_order <- c("April", "May", "June", "July", "August", "September",
                   "October", "November", "December", "January", "February",
                   "March")

tib_FY_CA<- get_FY_CA_data(raw_tib) %>% 
  add_GGC_field()

```

```{r historicalrates}

#list of all Councils containing tibbles for min,max, avg current values
#list separated into two sections (Code_9 and Standard), then by Council Area
all_rates <- get_prev_7yr_rates(tib_FY_CA, CNeeds_list, CA_of_interest, fydate) 
#create empty list to accept plots and tables
list_p <- vector(mode = "list", length = length(CA_of_interest))
list_t <- vector(mode = "list", length = length(CA_of_interest))

plot_table_func_list <- c("create_7yr_plot", "create_7yr_table")


for (count in seq_along(CA_of_interest)){ 
  arglist_i <- list(all_rates, index=count, CNeeds_string="Code 9", CA_of_interest = CA_of_interest[[count]])

list_p[[count]] <- do.call(plot_table_func_list[1], arglist_i)
list_t[[count]] <- do.call(plot_table_func_list[2], arglist_i)
}
```

```{r tabledata}
# data used for first 2 tabs and for summary stats
scot_ggc_code9_mon <- get_scot_ggc_CA_rates(tib=tib_FY_CA, CNeeds_string = "Code 9", fydate=fydate, mon=Report_month, FYTD_flag=FALSE)

scot_ggc_code9_fytd <- get_scot_ggc_CA_rates(tib=tib_FY_CA, CNeeds_string = "Code 9", fydate=fydate, mon=Report_month, FYTD_flag=TRUE)

scot_ggc_standard_mon <- get_scot_ggc_CA_rates(tib=tib_FY_CA, CNeeds_string = "Standard", fydate=fydate, mon=Report_month, FYTD_flag=FALSE)

scot_ggc_standard_fytd <- get_scot_ggc_CA_rates(tib=tib_FY_CA, CNeeds_string = "Standard", fydate=fydate, mon=Report_month, FYTD_flag=TRUE)
```

```{r summarystats}
# Code 9
## fytd : how many have rates above scot avg? which are they


## mon : how many have rates above scot avg? which are they


# Standard (as above)
## 

```


```{r }
#########################################################################################
###  Summary tibbles #####################################################################
##############################################################################
# Combines pc_change with previous time point and with last 5 yr Avg
mon = Report_month 

# tables arranged by rank
# Code 9
##  fytd rate and changes ordered by rank
fytd_code9_rate_changes <- get_summary_table(mon, CNeeds_string = "Code 9", FYTD = TRUE) %>% 
  arrange(Rank) %>% 
  select(-c(pc_change_Avg_5yr))

# fytd_code9_rankorder <- fytd_code9_rate_changes %>% select(CouncilArea)
# ##  monthly rate and changes ordered by rank of fytd table
# mon_code9_rate_changes <- fytd_code9_rankorder %>% 
#   left_join(.,get_summary_table(mon, CNeeds_string = "Code 9", FYTD = FALSE)) 
mon_code9_rate_changes <- get_summary_table(mon, CNeeds_string = "Code 9", FYTD = FALSE) %>% 
  arrange(Rank)


# Standard
##  fytd rate and changes
fytd_standard_rate_changes <- get_summary_table(mon, CNeeds_string = "Standard", FYTD = TRUE) %>% 
  arrange(Rank) %>% 
  select(-c(pc_change_Avg_5yr))

# fytd_standard_rankorder <- fytd_standard_rate_changes %>% select(CouncilArea)
# ##  monthly rate and changes ordered by rank of fytd table
# mon_standard_rate_changes <- fytd_standard_rankorder %>% 
#   left_join(.,get_summary_table(mon, CNeeds_string = "Standard", FYTD = FALSE)) 

mon_standard_rate_changes <- get_summary_table(mon, CNeeds_string = "Standard", FYTD = FALSE) %>% 
     arrange(Rank)                           

```




```{r appendixtables}
fytd_code9_app <- create_appendix(tib =tib_FY_CA, CNeeds_string = "Code 9", fydate=fydate, mon = Report_month, FYTD_flag = TRUE)

mon_code9_app <- create_appendix(tib =tib_FY_CA, CNeeds_string = "Code 9", fydate=fydate, mon = Report_month, FYTD_flag = FALSE)

fytd_standard_app <- create_appendix(tib =tib_FY_CA, CNeeds_string = "Standard", fydate=fydate, mon = Report_month, FYTD_flag = TRUE)

mon_standard_app <- create_appendix(tib =tib_FY_CA, CNeeds_string = "Standard", fydate=fydate, mon = Report_month, FYTD_flag = FALSE)
```

## Code 9 Results {.tabset}

### `r Report_month`

```{r}
create_CArate_plot(scot_ggc_code9_mon[[3]], CNeeds_string = "Code 9", fydate = fydate, mon = Report_month, FYTD_flag = FALSE,
                   g_rate = scot_ggc_code9_mon[[2]], s_rate = scot_ggc_code9_mon[[1]]) 

```

### FY to Date

```{r}
create_CArate_plot(scot_ggc_code9_mon[[3]], CNeeds_string = "Code 9", fydate = fydate, mon = Report_month, FYTD_flag = TRUE,
                   g_rate = scot_ggc_code9_mon[[2]], s_rate = scot_ggc_code9_mon[[1]]) 
```

### `r CA_of_interest[1]`

```{r}
list_p[[1]]
list_t[[1]]
  
```

### `r CA_of_interest[2]`

```{r}
list_p[[2]]
list_t[[2]]
  
```

### `r CA_of_interest[3]`

```{r}
list_p[[3]]
list_t[[3]]
  
```

### `r CA_of_interest[4]`

```{r}
list_p[[4]]
list_t[[4]]
  
```

### `r CA_of_interest[5]`

```{r}
list_p[[5]]
list_t[[5]]
  
```

### `r CA_of_interest[6]`

```{r}
list_p[[6]]
list_t[[6]]
  
```

### `r CA_of_interest[7]`

```{r}
list_p[[7]]
list_t[[7]]
  
```

### Summary Statistics – Delayed Discharge Bed Days (Code 9 Delays)

#### Financial Year to Date
A total of  `r get_written_summary_data(scot_ggc_code9_fytd)[[1]]` of 6 NHSGGC HSCPs have rates above the Scotland average. <br /> 
`r if (get_written_summary_data(scot_ggc_code9_fytd)[[1]]>0) {paste("They are",paste0( get_written_summary_data(scot_ggc_code9_fytd)[[2]], collapse = ", "))}`.


```{r}
gt(fytd_code9_rate_changes)
```

#### Current Month
A total of  `r get_written_summary_data(scot_ggc_code9_mon)[[1]]` of 6 NHSGGC HSCPs have rates above the Scotland average. <br /> 
`r if (get_written_summary_data(scot_ggc_code9_mon)[[1]]>0) {paste("They are",paste0( get_written_summary_data(scot_ggc_code9_mon)[[2]], collapse = ", "))}`.

```{r}
gt(mon_code9_rate_changes)
```

### Appendix 1 : HSCP Rankings for Financial Year to date `r fydate_text` (April 2021 to `r Report_month` `r Report_year`)

```{r}
gt(fytd_code9_app)
```

### Appendix 2: HSCP Rankings for `r Report_month` `r Report_year`
```{r}
gt(mon_code9_app)
```


## Standard Results {.tabset}

```{r}
for (count in seq_along(CA_of_interest)){ 
  arglist_i <- list(all_rates, index=count, CNeeds_string="Standard", CA_of_interest = CA_of_interest[count])

list_p[[count]] <- do.call(plot_table_func_list[1], arglist_i)
list_t[[count]] <- do.call(plot_table_func_list[2], arglist_i)
}
```

### `r Report_month`

```{r}
create_CArate_plot(scot_ggc_standard_mon[[3]], CNeeds_string = "Standard", fydate = fydate, mon = Report_month, FYTD_flag = FALSE,
                   g_rate = scot_ggc_standard_mon[[2]], s_rate = scot_ggc_standard_mon[[1]]) 
```

### FY to Date

```{r}
create_CArate_plot(scot_ggc_standard_fytd[[3]], CNeeds_string = "Standard", fydate = fydate, mon = Report_month, FYTD_flag = TRUE,
                   g_rate = scot_ggc_standard_fytd[[2]], s_rate = scot_ggc_standard_fytd[[1]]) 
```

### `r CA_of_interest[1]`

```{r}
list_p[[1]]
list_t[[1]]
  
```

### `r CA_of_interest[2]`

```{r}
list_p[[2]]
list_t[[2]]
  
```

### `r CA_of_interest[3]`

```{r}
list_p[[3]]
list_t[[3]]
  
```

### `r CA_of_interest[4]`

```{r}
list_p[[4]]
list_t[[4]]
  
```

### `r CA_of_interest[5]`

```{r}
list_p[[5]]
list_t[[5]]
  
```

### `r CA_of_interest[6]`

```{r}
list_p[[6]]
list_t[[6]]
  
```

### `r CA_of_interest[7]`

```{r}
list_p[[7]]
list_t[[7]]
  
```

### Summary Statistics – Delayed Discharge Bed Days (Standard Delays)

#### Financial Year to Date
A total of  `r get_written_summary_data(scot_ggc_standard_fytd)[[1]]` of 6 NHSGGC HSCPs have rates above the Scotland average. <br /> 
`r if (get_written_summary_data(scot_ggc_standard_fytd)[[1]]>0) {paste("They are",paste0( get_written_summary_data(scot_ggc_standard_fytd)[[2]], collapse = ", "))}`.


```{r}
gt(fytd_standard_rate_changes)
```

#### Current Month
A total of  `r get_written_summary_data(scot_ggc_standard_mon)[[1]]` of 6 NHSGGC HSCPs have rates above the Scotland average. <br /> `r if (get_written_summary_data(scot_ggc_standard_mon)[[1]]>0) {paste("They are",paste0( get_written_summary_data(scot_ggc_standard_mon)[[2]], collapse = ", "))}`.
```{r}
gt(mon_standard_rate_changes)
```

### Appendix 1 : HSCP Rankings for Financial Year to date `r fydate_text` (April 2021 to `r Report_month` `r Report_year`)

```{r}
gt(fytd_standard_app)
```

### Appendix 2: HSCP Rankings for `r Report_month` `r Report_year`
```{r}
gt(mon_standard_app)
```


