---
title: "Untitled"
author: "Andrew Saul"
date: "14/02/2022"
output: html_document
editor_options: 
  chunk_output_type: console
---

- Need to check 20/21 FY to date rates
- Need to get 5yr avg rates


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.width = 10, fig.height = 6)
```


```{r include = "FALSE"} 
if(!require(librarian)){
  install.packages("librarian")
  library(librarian)
}

librarian::shelf(tidyverse, here, fs, rvest ,xml2, openxlsx, lubridate, readxl, janitor, glue, rlang, plotly, ggtext, kableExtra)
source(here::here("scripts", "my_funcs.R"))
source(here::here("scripts", "populations.R"))
```

```{r variables}
Report_month <- "January"
Report_year <- 2022

# Current FY
fydate <- convert_calender_to_FY(Report_year, Report_month)

# council areas of interest
CA_of_interest <- c("Scotland", "East Dunbartonshire", "East Renfrewshire", "Glasgow City", "Inverclyde", "Renfrewshire", "West Dunbartonshire") %>% 
  set_names(.)

CA_no_Scotland <- c("East Dunbartonshire", "East Renfrewshire", "Glasgow City", "Inverclyde", "Renfrewshire", "West Dunbartonshire") %>% 
  set_names(.)

CNeeds_list <- c("Code 9", "Standard") %>%
  set_names(.)
```


```{r historical-stats}
# getLAPops acquires pop data stored in an .rds file
#find pops for ages>= 18 for all LAs and Scotland
# NO SCOTLAND POP DATA WITH THIS .RDS

# no data available for mid-pop estimate for 2021.  
# locf (last observation carried forward) utilised from 2020 for 2021
#Scotland pop values created by summing all CouncilAreas.
LA_pop_18plus <- getLAPops(age_lowest = 18)

```

```{r download-NRS-recent-data}
#file downloaded from NRS website if filename not present in data folder
data_filename <- "beddays"
#if(!file_exists(here::here("data", glue("{data_filename}.xlsx")))){
download_data(filename = data_filename, month=Report_month, year=Report_year)

```

```{r convert-to-tibbles}
# save pathname of beddays xlsx file to object 
xl_file <- here::here("data", glue("{data_filename}.xlsx"))

#create a single tibble containing both healthboard and LA data, as "Scotland" located in HB... sheets. Only "Scotland" kept from HB... sheets 
# change format of FY (eg 1718)to year of start FY (2017)
raw_tib <- map_dfr(create_sheetname_vector(xl_file), # vector of LA and HB data from FY 12/13 until 21/22
              ~create_FY_authority(xl_file, sheet_name = .x)) 

######################################################################################
#create tibble with FY to date 
# tib_fytd <- raw_tib %>% 
#   select("CouncilArea", "AgeGroup", "ComplexNeedsFlag", "FYToDate", "FY", "FY_begin") %>% 
#   rename(Counts = FYToDate) %>% 
#   add_GGC_field()

######################################################################################
#create tibble with Month/Year Counts
# used to 1- select columns for pivoting & 2- set order of months
month_order <- c("April", "May", "June", "July", "August", "September",
                   "October", "November", "December", "January", "February",
                   "March")

tib_FY_CA<- get_FY_CA_data(raw_tib) %>% 
  add_GGC_field()

```

```{r historicalrates}

#list of all Councils containing tibbles for min,max, avg current values
#list separated into two sections (Code_9 and Standard), then by Council Area
all_rates <- get_prev_7yr_rates(tib_FY_CA, CNeeds_list, CA_of_interest, fydate) 
#create empty list to accept plots and tables
list_p <- vector(mode = "list", length = length(CA_of_interest))
list_t <- vector(mode = "list", length = length(CA_of_interest))

plot_table_func_list <- c("create_7yr_plot", "create_7yr_table")


for (count in seq_along(CA_of_interest)){ 
  arglist_i <- list(all_rates, index=count, CNeeds_string="Code 9", CA_of_interest = CA_of_interest[[count]])

list_p[[count]] <- do.call(plot_table_func_list[1], arglist_i)
list_t[[count]] <- do.call(plot_table_func_list[2], arglist_i)
}

#########################################################################################
###  Summary tibbles #####################################################################
##############################################################################
# Combines pc_change with previous time point and with last 5 yr Avg
mon = Report_month

# Combines pc_change with previous time point and with last 5 yr Avg

# Code 9
##  fytd rate and changes ordered by rank
fytd_code9_rate_changes <- get_summary_table(mon, CNeeds_string = "Code 9", FYTD = TRUE) %>% 
  arrange(Rank) %>% 
  select(-c(pc_change_Avg_5yr))

fytd_code9_rankorder <- fytd_code9_rate_changes %>% select(CouncilArea)
##  monthly rate and changes ordered by rank of fytd table
mon_code9_rate_changes <- fytd_code9_rankorder %>% 
  left_join(.,get_summary_table(mon, CNeeds_string = "Code 9", FYTD = FALSE)) 


# Standard
##  fytd rate and changes
fytd_standard_rate_changes <- get_summary_table(mon, CNeeds_string = "Standard", FYTD = TRUE) %>% 
  arrange(Rank) %>% 
  select(-c(pc_change_Avg_5yr))

fytd_standard_rankorder <- fytd_standard_rate_changes %>% select(CouncilArea)
##  monthly rate and changes ordered by rank of fytd table
mon_standard_rate_changes <- fytd_standard_rankorder %>% 
  left_join(.,get_summary_table(mon, CNeeds_string = "Standard", FYTD = FALSE)) 

```

```{r appendixtables}
fytd_code9_app <- create_appendix(tib =tib_FY_CA, CNeeds_string = "Code 9", fydate=fydate, mon = Report_month, FYTD_flag = TRUE)

mon_code9_app <- create_appendix(tib =tib_FY_CA, CNeeds_string = "Code 9", fydate=fydate, mon = Report_month, FYTD_flag = FALSE)

fytd_standard_app <- create_appendix(tib =tib_FY_CA, CNeeds_string = "Standard", fydate=fydate, mon = Report_month, FYTD_flag = TRUE)

mon_standard_app <- create_appendix(tib =tib_FY_CA, CNeeds_string = "Standard", fydate=fydate, mon = Report_month, FYTD_flag = FALSE)
```

## Code 9 Results {.tabset}

### `r Report_month`

```{r}
create_current_rateplot(tib=tib_FY_CA, CNeeds_string = "Code 9", fydate = fydate, mon = Report_month, FYTD_flag = FALSE)

```

### FY to Date

```{r}
create_current_rateplot(tib=tib_FY_CA, CNeeds_string = "Code 9", fydate = fydate, mon=Report_month, FYTD_flag = TRUE)
```

### `r CA_of_interest[1]`

```{r}
list_p[[1]]
list_t[[1]]
  
```

### `r CA_of_interest[2]`

```{r}
list_p[[2]]
list_t[[2]]
  
```

### `r CA_of_interest[3]`

```{r}
list_p[[3]]
list_t[[3]]
  
```

### `r CA_of_interest[4]`

```{r}
list_p[[4]]
list_t[[4]]
  
```

### `r CA_of_interest[5]`

```{r}
list_p[[5]]
list_t[[5]]
  
```

### `r CA_of_interest[6]`

```{r}
list_p[[6]]
list_t[[6]]
  
```

### `r CA_of_interest[7]`

```{r}
list_p[[7]]
list_t[[7]]
  
```

```{r}

```


## Standard Results {.tabset}

```{r}
for (count in seq_along(CA_of_interest)){ 
  arglist_i <- list(all_rates, index=count, CNeeds_string="Standard", CA_of_interest = CA_of_interest[count])

list_p[[count]] <- do.call(plot_table_func_list[1], arglist_i)
list_t[[count]] <- do.call(plot_table_func_list[2], arglist_i)
}
```

### `r Report_month`

```{r}
create_current_rateplot(tib=tib_FY_CA, CNeeds_string = "Standard", fydate = "2122", mon = Report_month)
```

### FY to Date

```{r}
create_current_rateplot(tib=tib_FY_CA, CNeeds_string = "Standard", fydate = 2122, mon=Report_month, FYTD_flag = TRUE)
```

### `r CA_of_interest[1]`

```{r}
list_p[[1]]
list_t[[1]]
  
```

### `r CA_of_interest[2]`

```{r}
list_p[[2]]
list_t[[2]]
  
```

### `r CA_of_interest[3]`

```{r}
list_p[[3]]
list_t[[3]]
  
```

### `r CA_of_interest[4]`

```{r}
list_p[[4]]
list_t[[4]]
  
```

### `r CA_of_interest[5]`

```{r}
list_p[[5]]
list_t[[5]]
  
```

### `r CA_of_interest[6]`

```{r}
list_p[[6]]
list_t[[6]]
  
```

### `r CA_of_interest[7]`

```{r}
list_p[[7]]
list_t[[7]]
  
```



