---
title: "NHSGGC Delayed Discharge Bed Days Monthly Performance Report"
subtitle: "`r params$Report_month` `r params$Report_year`"
output: html_document
params:
  Report_month: "March"
  Report_year: 2022
  earliest_historical_fy: "2017/18"
  most_recent_historical_fy : "2019/20"
editor_options: 
  chunk_output_type: console
---

Note they way the number of GGCs above scotland level were calculated in Tables 1,2,3,4

have created all_prev_rates : table with prev rates, raw data with ordered factor date (? necessary)
```{r setup, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.width = 10, fig.height = 6)
```

```{r include = "FALSE"} 
if(!require(librarian)){
  install.packages("librarian")
  library(librarian)
}

librarian::shelf(tidyverse, here, fs, rvest ,xml2, openxlsx, lubridate, readxl, janitor, glue, plotly, ggtext,  gt, rlang)
source(here::here("scripts", "march22_funcs.R"))
source(here::here("scripts", "populations.R"))
```

```{r}
# for use in Appendix titles and CA_rate_plots
if(params$Report_month %in% c("January", "Februrary", "March")){
      year_begin <- params$Report_year-1
    } else {
      year_begin <- params$Report_year
    }
```

**NOTES**

Data Source:

```{r results='asis', echo=FALSE}
http_address <- glue("https://publichealthscotland.scot/publications/delayed-discharges-in-nhsscotland-monthly/delayed-discharges-in-nhsscotland-monthly-figures-for-{params$Report_month}-{params$Report_year}/#section-1")

```

[Delayed discharges in NHSScotland monthly up to `r params$Report_month` `r params$Report_year`.](`r http_address`)   
<br>
Figures reflect **Code 9 delays**  and **standard delays** (excluding code 9s) for those aged 18+ and are based on HSCP of
residence. Code 9 delays include delays for Adults with Incapacity (AWIs).    
<br>
Greater Glasgow and Clyde figures (GGC HSCPs) are the sum of all six GGC HSCPs and are based on residents of NHSGGC only.  
<br>
Rates are calculated using the NRS Mid-Year Population Estimates for those aged
18+ (2020 population estimates are used for calculating the 2021/22 rates).  
<br>
Scotland figures are an aggregate of local authority data. ‘Other’ local authority
does not apply to Code 9 delays.  


```{r variables}

# Current FY in format "yyyy/yy"
# fydate <- convert_calender_to_FY(params$Report_year, params$Report_month)
# year_begin <- seperate_years_by_slash(fydate)

# council areas of interest
 CA_of_interest <- c("Scotland", "East Dunbartonshire", "East Renfrewshire", "Glasgow City", "Inverclyde", "Renfrewshire", "West Dunbartonshire") %>% set_names()

# ---------------------------------------------------------------------------------------
CA_no_Scotland <- c("East Dunbartonshire", "East Renfrewshire", "Glasgow City", "Inverclyde", "Renfrewshire", "West Dunbartonshire") %>% 
  set_names(.)
# ---------------------------------------------------------------------------------------
delay_reasons_list <- c("All code 9 delay reasons", "All standard") #%>%
 # set_names(.)
```



```{r historical-stats}
# getLAPops acquires pop data stored in an .rds file
#find pops for ages>= 18 for all LAs and Scotland
# NO SCOTLAND POP DATA WITH THIS .RDS

# no data available for mid-pop estimate for 2021 nor 2022.  
# locf (last observation carried forward) utilised from 2020 for 2021 and 2022
#Scotland pop values created by summing all CouncilAreas.
LA_pop_18plus <- getLAPops(age_lowest = 18) 


```

```{r download-NRS-recent-data}

#downloading two excel files that contain standard and code9 delays respectively
download_data(month=params$Report_month, year=params$Report_year)

```

```{r convert-to-tibbles, message=FALSE}
# Excel data files names
code9_xl_name <- here::here("data", glue("code9.xlsx"))

standard_xl_name <- here::here("data", glue("standard.xlsx"))

# <create_FY_authority> function extracts relevant data from NRS excel sheet and stores
# as a tibble.
code9_obj <- create_FY_authority(xl_file = code9_xl_name, sheet_name = "data", delay_reason = "All code 9 delay reasons")
#  The age_groups 18-74 and 75+ are aggregated to produce results for 18+ population.
#  Within the Excel files, some 18+ age_group rows for Scotland are missing


standard_ojb <- create_FY_authority(xl_file = standard_xl_name, sheet_name = "data_1", delay_reason = "All standard")
# Create a common tibble containing both "standard"" and "code9" <delay reasons> 

# excludes FY 2016/17 and 2020/21

df_main <- create_main_tibble(code9_obj, standard_ojb) 

# current_fy used for table header outputs
current_fy <- as.character(select_current_fy(df_main)) 

#check that no NA obd values are present.  Send message if obd NAs are present
# and remove inaccurate df_main tibble from environment to cause knitr to error
if(count(df_main %>% filter(is.na(counts)))>0){
  rm(df_main)
  stop("There are NA count values in the dataset.  Please recheck")
  
} 

```


```{r historicalrates}

# <rates_permonth> function: 
# 1st list: tibble containing data from "earliest_historical_fy" until current year 
# 2nd list: Names of fin_yrs comprising data in list 1

rates_permonth <- get_rates_years_of_interest(df_main, delay_reasons_list, CA_of_interest)

#create empty list to accept plots and tables
list_p <- vector(mode = "list", length = length(CA_of_interest))
list_t <- vector(mode = "list", length = length(CA_of_interest))

plot_table_func_list <- c("create_regional_plot", "create_current_FY_tables")


for (count in seq_along(CA_of_interest)){ 
  arglist_i <- list(rates_permonth, index=count, delay_reason=delay_reasons_list[[1]], CA_of_interest = CA_of_interest[count])

list_p[[count]] <- do.call(plot_table_func_list[1], arglist_i)
list_t[[count]] <- do.call(plot_table_func_list[2], arglist_i)
}
```

```{r tab12summaryappendix}
# data used for first 2 tab- plots and for summary stats
## each obj contains a list of the 1-scot rate, 2-ggc rate and 3-all individual HSCP rates
code9_mon <- create_bedrate_list(tib=df_main, delay_reason = delay_reasons_list[1], mon=params$Report_month, FYTD_flag=FALSE)

code9_fytd <- create_bedrate_list(tib=df_main, delay_reason = delay_reasons_list[1], mon=params$Report_month, FYTD_flag=TRUE)

standard_mon <- create_bedrate_list(tib=df_main, delay_reason = delay_reasons_list[2], mon=params$Report_month, FYTD_flag=FALSE)

standard_fytd <- create_bedrate_list(tib=df_main, delay_reason = delay_reasons_list[2], mon=params$Report_month, FYTD_flag=TRUE)
```


```{r }
#########################################################################################
###  Summary tibbles #####################################################################
##############################################################################
# Combines pc_change with previous time point and with last 5 yr Avg

# tables arranged by rank
# Code 9
##  fytd rate and changes ordered by rank
fytd_code9_rate_changes <- get_summary_table(tib=df_main, mon = params$Report_month, delay_reason = "All code 9 delay reasons", FYTD_flag = TRUE) %>% 
  arrange(Rank) %>% 
  select(-c(pc_change_Avg_5yr))

# fytd_code9_rankorder <- fytd_code9_rate_changes %>% select(CouncilArea)
# ##  monthly rate and changes ordered by rank of fytd table
# mon_code9_rate_changes <- fytd_code9_rankorder %>% 
#   left_join(.,get_summary_table(mon, CNeeds_string = "Code 9", FYTD = FALSE)) 
mon_code9_rate_changes <- get_summary_table(tib=df_main, mon = params$Report_month, delay_reason = "All code 9 delay reasons", FYTD_flag = FALSE) %>% 
  arrange(Rank)


# Standard
##  fytd rate and changes
fytd_standard_rate_changes <- get_summary_table(tib=df_main, mon = params$Report_month, delay_reason = "All standard", FYTD = TRUE) %>% 
  arrange(Rank) %>% 
  select(-c(pc_change_Avg_5yr))

# fytd_standard_rankorder <- fytd_standard_rate_changes %>% select(CouncilArea)
# ##  monthly rate and changes ordered by rank of fytd table
# mon_standard_rate_changes <- fytd_standard_rankorder %>% 
#   left_join(.,get_summary_table(mon, CNeeds_string = "Standard", FYTD = FALSE)) 

mon_standard_rate_changes <- get_summary_table(tib=df_main, mon = params$Report_month, delay_reason = "All standard", FYTD = FALSE) %>% 
     arrange(Rank)                           

```




```{r appendixtables}
fytd_code9_app <- create_appendix(tib =df_main, delay_reason = delay_reasons_list[1], mon = params$Report_month, FYTD_flag = TRUE)

mon_code9_app <- create_appendix(tib =df_main, delay_reason = delay_reasons_list[1], mon = params$Report_month, FYTD_flag = FALSE)

fytd_standard_app <- create_appendix(tib =df_main, delay_reason = delay_reasons_list[2], mon = params$Report_month, FYTD_flag = TRUE)

mon_standard_app <- create_appendix(tib =df_main, delay_reason = delay_reasons_list[2], mon = params$Report_month, FYTD_flag = FALSE)
```

## Code 9 Delays {.tabset}

### `r params$Report_month`

```{r}
create_CArate_plot(code9_mon[[3]], delay_reason = delay_reasons_list[[1]],  mon = params$Report_month, FYTD_flag = FALSE,
                   g_rate = code9_mon[[2]], s_rate = code9_mon[[1]]) 

```

### FY to Date

```{r}
create_CArate_plot(code9_fytd[[3]], delay_reason = delay_reasons_list[[1]],  mon = params$Report_month, FYTD_flag = TRUE, g_rate = code9_fytd[[2]], s_rate = code9_fytd[[1]]) 
```

### `r CA_of_interest[1]`

```{r message=FALSE}
list_p[[1]]
list_t[[1]]
  
```

### `r CA_of_interest[2]`

```{r message=FALSE}
list_p[[2]]
list_t[[2]]
  
```

### `r CA_of_interest[3]`

```{r message=FALSE}
list_p[[3]]
list_t[[3]]
  
```

### `r CA_of_interest[4]`

```{r message=FALSE}
list_p[[4]]
list_t[[4]]
  
```

### `r CA_of_interest[5]`

```{r message=FALSE}
list_p[[5]]
list_t[[5]]
  
```

### `r CA_of_interest[6]`

```{r message=FALSE}
list_p[[6]]
list_t[[6]]
  
```

### `r CA_of_interest[7]`

```{r message=FALSE}
list_p[[7]]
list_t[[7]]
  
```

### Summary Statistics 

#### Table 1 

A total of  `r get_written_summary_data(code9_fytd)[[1]]` of 6 NHSGGC HSCPs have rates above the Scotland average. <br /> 
`r if (get_written_summary_data(code9_fytd)[[1]]>0) {paste("They are",paste0( get_written_summary_data(code9_fytd)[[2]], collapse = ", "))}`.


```{r}
create_fytd_dd_table(tib =fytd_code9_rate_changes, title_name = "**FYTD – Delayed Discharge Bed Days (Code 9 Delays)**")

```

***

#### Table 2

A total of  `r get_written_summary_data(code9_mon)[[1]]` of 6 NHSGGC HSCPs have rates above the Scotland average. <br /> 
`r if (get_written_summary_data(code9_mon)[[1]]>0) {paste("They are",paste0( get_written_summary_data(code9_mon)[[2]], collapse = ", "))}`.

```{r}
create_month_dd_table(tib =mon_code9_rate_changes, title_name = "**{params$Report_month} {params$Report_year}– Delayed Discharge Bed Days (Code 9 Delays)**")
```

### Appendix 1 : HSCP Rankings for Financial Year to date `r current_fy` 

```{r}
create_appendix1(tib=fytd_code9_app, title_name = "**HSCP Rankings for Financial Year to date {year_begin} (April 2021 to {params$Report_month} {params$Report_year})**") 

```

### Appendix 2: HSCP Rankings for `r params$Report_month` `r params$Report_year`
```{r}
create_appendix2(tib=mon_code9_app, title_name = "**Appendix 2: HSCP Rankings for {params$Report_month} {params$Report_year}**")
```


## Standard Delays {.tabset}

```{r}
for (count in seq_along(CA_of_interest)){ 
  arglist_i <- list(rates_permonth, index=count, delay_reason=delay_reasons_list[[2]], CA_of_interest = CA_of_interest[count])

list_p[[count]] <- do.call(plot_table_func_list[1], arglist_i)
list_t[[count]] <- do.call(plot_table_func_list[2], arglist_i)
}
```

### `r params$Report_month`

```{r}
create_CArate_plot(standard_mon[[3]], delay_reason = delay_reasons_list[[2]],  mon = params$Report_month, FYTD_flag = FALSE,
                   g_rate = standard_mon[[2]], s_rate = standard_mon[[1]]) 

```

### FY to Date

```{r}
create_CArate_plot(standard_fytd[[3]], delay_reason = delay_reasons_list[[2]],  mon = params$Report_month, FYTD_flag = TRUE, g_rate = standard_fytd[[2]], s_rate = standard_fytd[[1]]) 

```

### `r CA_of_interest[1]`

```{r message=FALSE}
list_p[[1]]
list_t[[1]]
  
```

### `r CA_of_interest[2]`

```{r message=FALSE}
list_p[[2]]
list_t[[2]]
  
```

### `r CA_of_interest[3]`

```{r message=FALSE}
list_p[[3]]
list_t[[3]]
  
```

### `r CA_of_interest[4]`

```{r message=FALSE}
list_p[[4]]
list_t[[4]]
  
```

### `r CA_of_interest[5]`

```{rmessage=FALSE}
list_p[[5]]
list_t[[5]]
  
```

### `r CA_of_interest[6]`

```{r message=FALSE}
list_p[[6]]
list_t[[6]]
  
```

### `r CA_of_interest[7]`

```{r message=FALSE}
list_p[[7]]
list_t[[7]]
  
```

### Summary Statistics

#### Table 3

A total of  `r get_written_summary_data(standard_fytd)[[1]]` of 6 NHSGGC HSCPs have rates above the Scotland average. <br /> 
`r if (get_written_summary_data(standard_fytd)[[1]]>0) {paste("They are",paste0( get_written_summary_data(standard_fytd)[[2]], collapse = ", "))}`.


```{r}
create_fytd_dd_table(tib =fytd_standard_rate_changes, title_name = "**FYTD – Delayed Discharge Bed Days (Standard Delays)**")
```

***

#### Table 4

A total of  `r get_written_summary_data(standard_mon)[[1]]` of 6 NHSGGC HSCPs have rates above the Scotland average. <br /> `r if (get_written_summary_data(standard_mon)[[1]]>0) {paste("They are",paste0( get_written_summary_data(standard_mon)[[2]], collapse = ", "))}`.

```{r}
create_month_dd_table(tib =mon_standard_rate_changes, title_name = "**{params$Report_month} {params$Report_year}– Delayed Discharge Bed Days (Standard Delays)**")

```

### Appendix 1 : HSCP Rankings for Financial Year to date 20`r current_fy` 

```{r}
create_appendix1(tib=fytd_standard_app, title_name = "**HSCP Rankings for Financial Year to date {current_fy} (April 2021 to {params$Report_month} {params$Report_year})**")

```

### Appendix 2: HSCP Rankings for `r params$Report_month` `r params$Report_year`
```{r}
create_appendix2(tib=mon_standard_app, title_name = "**Appendix 2: HSCP Rankings for {params$Report_month} {params$Report_year}**")
```
